% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2014 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{mdframed}
\usepackage{color}
\usepackage{hyperref}
\definecolor{mygray}{gray}{0.90}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%\mdfsetup{innerleftmargin=8pt}
%\mdfsetup{hidealllines=true}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
%\newcommand{\resheading}[1]{{\begin{minipage}{\textwidth}{\colorbox{mygray}{\large \textbf{#1 \vphantom{p\^{E}}}}}\end{minipage}}}
\newcommand{\resheading}[1]{{\begin{mdframed}[backgroundcolor=mygray]{\large \textbf{#1}}\end{mdframed}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
\newcommand{\restitle}[2]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
\end{tabular*}}
\newcommand{\ressubtitle}[2]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textit{#1} & \textit{#2} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Keen Yee Liau}  & (734) 747-0922 \\
546 Main St. Apt 827 &  kyliau@umich.edu                                \\
New York, NY 10044 & \href{http://kyliau.github.io/}{http://kyliau.github.io} \\
\end{tabular*}
\\

\vspace{0.1in}
%\hrules
%\vspace{0.05in}

\resheading{Education}
\begin{itemize}
\item
	\restitle{University of Michigan}{Ann Arbor, MI}
	\ressubtitle{Master of Science, Aerospace Engineering}{Sep. 2012 - May 2014}
	\begin{itemize}
		\resitem{Focused on computational methods and flight software.}
	\end{itemize}
	\ressubtitle{Bachelor of Science, Aerospace Engineering}{Jan. 2008 - May 2011}
	\begin{itemize}
		\resitem{\textit{Summa Cum Laude}}
		\resitem{Minor in signal processing and control systems}
		\resitem{Five terms \textit{University Honor}, five terms \textit{College of Engineering Dean's List}}
	\end{itemize}
\item
	\restitle{Stanford University}{Stanford, CA}
	\ressubtitle{Certificate of Completion in Computer Science}{June 2013 - Aug. 2013}
	\begin{itemize}
		\resitem{Design and Analysis of Algorithms, Client-side Internet Technologies}
	\end{itemize}
\end{itemize}


\resheading{Work Experience}
\begin{itemize}

\item
	\restitle{Bloomberg LP}{New York, NY}
	\ressubtitle{Infrastructure Software Engineer}{Dec. 2014 - Present}
	\begin{itemize}
		\resitem{Work on a new version release system for the next-generation Bloomberg Terminal.}
		\resitem{Provide a versatile platform that significantly enhances developer experience of deploying different versions of software to different environments by implementing key features in the back-end service and revamping the front-end UI that facilitates the entire release management process.}
		\resitem{Responsible for the resource access validation project, a permissioning system that allows developers to restrict and monitor usage of their API.}
	\end{itemize}

\item
	\restitle{FlightAware}{Houston, TX}
	\ressubtitle{Intern}{June 2014 - Oct. 2014}
	\begin{itemize}
		\resitem{Improved the reliability and accuracy of FlightAware API by developing a comprehensive test suite using Python \emph{unittest} framework.}
	\end{itemize}

\item
	\restitle{Stress Analysis and Design Aerospace}{Kuala Lumpur, Malaysia}
	\ressubtitle{Structural Engineer}{Sep. 2011 - July 2012}
	\begin{itemize}
		\resitem{Airbus A350XWB Flight Test Program: Co-authored six stress dossiers for static analysis of Flight Test Instruments (FTI) using classical methods and finite element modeling.}
		\resitem{Developed a program to estimate the lifespan of an aircraft by analyzing fatigue and cyclic loads on the wings.}
	\end{itemize}

\end{itemize}

%\pagebreak
\resheading{Personal Project}

\begin{itemize}
\item
	%\restitle{Expense Tracker}{\url{http://expense--tracker.appspot.com/}}
	\restitle{Expense Tracker}{\href{http://expense--tracker.appspot.com/}{http://expense-{}-tracker.appspot.com}}
	\vspace{-6pt}
	\begin{itemize}
		\resitem{A simple and responsive website that calculates and keeps track of group travel costs.}
		\resitem{Developed using Python and webapp2 framework, hosted on Google App Engine.}
	\end{itemize}
\end{itemize}

%\begin{description}
%\item[Expense Tracker]
%a website to keep track of group travel costs. Developed using Python and webapp2 framework, hosted on Google App Engine.
%\end{description}

\resheading{Skills}

\begin{description}
\item[Programming:]
C{}\verb!++!, Javascript
%\item[Tools:]
%Vim, Git
\item[Operating Systems:]
Windows, Mac OS X, Linux
\item[Languages:]
English, Chinese (Mandarin), and Malay
\end{description}

\end{document}
